---
title: "Construct MTPL Datasets"
author: "Mick Cooney <mickcooney@gmail.com>"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    theme: spacelab
    highlight: pygments
    number_sections: TRUE
    toc: TRUE
    toc_depth: 3
    toc_float:
      smooth_scroll: FALSE
  pdf_document: default
---


```{r import_libraries, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(tidy       = FALSE,
                      cache      = FALSE,
                      warning    = FALSE,
                      message    = FALSE,
                      fig.height =     8,
                      fig.width  =    11
                     )

library(conflicted)
library(tidyverse)
library(scales)
library(cowplot)
library(magrittr)
library(rlang)
library(purrr)
library(vctrs)
library(fs)
library(forcats)
library(snakecase)
library(lubridate)

library(CASdatasets)

source("custom_functions.R")

resolve_conflicts(c("magrittr", "rlang", "dplyr", "readr", "purrr", "ggplot2"))


options(width = 80L,
        warn  = 1,
        mc.cores = parallel::detectCores()
        )

theme_set(theme_cowplot())

set.seed(42)
```



# Load MTPL Data

We want to load the MTPL dataset from the `CASdatasets` package - this data
contains both the policy and claim data.

```{r load_data, echo=TRUE}
data(freMTPLfreq)
data(freMTPLsev)

data(freMTPL2freq)
data(freMTPL2sev)
```

We now take both datasets and try to construct a single dataset in each case.

To do this, we need to check the structure of all these.


```{r check_first_dataset, echo=TRUE}
freMTPLfreq %>% glimpse()
freMTPLsev  %>% glimpse()
```

---

We also want to check the structure of the second dataset.

```{r check_second_dataset, echo=TRUE}
freMTPL2freq %>% glimpse()
freMTPL2sev  %>% glimpse()
```



# Reconstruct Data

Both sets of data has ID columns of mis-matched types - `PolicyID` and `IDpol`
- so we convert all of them to characters for the purposes of joining them

```{r reconstruct_first_data_cols, echo=TRUE}
freq1_tbl <- freMTPLfreq %>%
  as_tibble() %>%
  mutate(PolicyID = PolicyID %>% as.character())

freq1_tbl %>% glimpse()

sev1_tbl <- freMTPLsev %>%
  as_tibble() %>%
  mutate(PolicyID = PolicyID %>% as.character())

sev1_tbl %>% glimpse()
```


We now want to fix the second dataset in a similar fashion.

```{r reconstruct_second_data_cols, echo=TRUE}
freq2_tbl <- freMTPL2freq %>%
  as_tibble() %>%
  mutate(IDpol = IDpol %>% as.character())

freq2_tbl %>% glimpse()

sev2_tbl <- freMTPL2sev %>%
  as_tibble() %>%
  mutate(IDpol = IDpol %>% as.character())

sev2_tbl %>% glimpse()
```


# Check Matching IDs

We want to ensure that all data in the both sets have corresponding values in
the other dataset - in particular, we want to ensure that all claim amounts
match the frequency amounts.

```{r match_first_claim_amounts, echo=TRUE}
sev1_tbl %>%
  anti_join(freq1_tbl, by = "PolicyID") %>%
  glimpse()
```

The first dataset has no mismatched claims as this table has no rows.

We now move on to the second dataset:

```{r match_second_claim_amounts, echo=TRUE}
sev2_tbl %>%
  anti_join(freq2_tbl, by = "IDpol") %>%
  glimpse()

sev2_tbl %>%
  anti_join(freq2_tbl, by = "IDpol") %>%
  count(IDpol, name = "claim_count") %>%
  glimpse()
```

We see we have almost 200 claims that do not have a matching policy, but those
claims are associated with only six IDs. This poses a conundrum for our
modelling that we will need to address later.

For now though, we just add these `IDpol` values to our frequency table for
now.

```{r add_missing_policies, echo=TRUE}
missing_tbl <- sev2_tbl %>%
  anti_join(freq2_tbl, by = "IDpol") %>%
  select(IDpol) %>%
  distinct()

freq2_tbl <- list(
    freq2_tbl %>% select(-ClaimNb),
    missing_tbl
    ) %>%
  bind_rows()

freq2_tbl %>% glimpse()
```


# Construct Datasets

We now construct our datasets to combine both policy and claim data so we
can analyse it.


```{r construct_first_dataset, echo=TRUE}
modelling1_data_tbl <- freq1_tbl %>%
  nest_join(sev1_tbl, by = "PolicyID", name = "sev_data") %>%
  select(-ClaimNb) %>%
  set_names(names(.) %>% to_snake_case()) %>%
  mutate(claim_count = map_int(sev_data, nrow))

modelling1_data_tbl %>% glimpse()
```

Having constructed the first dataset, we now perform a similar set of
operations to construct the second set of data.

```{r construct_second_dataset, echo=TRUE}
modelling2_data_tbl <- freq2_tbl %>%
  nest_join(sev2_tbl, by = "IDpol", name = "sev_data") %>%
  set_names(names(.) %>% to_snake_case()) %>%
  rename(pol_id = i_dpol) %>%
  mutate(
    pol_id      = pol_id %>% as.character(),
    claim_count = map_int(sev_data, nrow)
    )
  
modelling1_data_tbl %>% glimpse()
```



# Write to Disk

We now save both datasets to disk.

```{r write_data_to_disk, echo=TRUE}
modelling1_data_tbl %>% write_rds("data/modelling1_data_tbl.rds")

modelling2_data_tbl %>% write_rds("data/modelling2_data_tbl.rds")
```
